The SMT Competition 2015--2018

### 2019-08-30 2018/report/SMT-COMP.tex
Report: Tweak winners table layout.
Report: Update text after table updates.

@@

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
  \caption{VBS on common benchmarks 2015--2018 of all logics in the
    \maintrack with a time limit of \SI{1200}{s}.  Number of common
    benchmarks is indicated with a gray vertical line.}
  \label{fig:progress-all}
\end{figure}

\begin{figure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2014-2015.pdf}}
    \caption{2014 vs.~2015}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2016.pdf}}
    \caption{2015 vs.~2016}
  \end{subfigure}
  \\[2ex]
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2016-2017.pdf}}
    \caption{2016 vs.~2017}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2017-2018.pdf}}
    \caption{2017 vs.~2018}
  \end{subfigure}
  \caption{VBS on common benchmarks for pairs of years of all logics
    in the \maintrack with a time limit of \SI{1200}{s}.  Number of
    common benchmarks is indicated with a gray vertical line.}
  \label{fig:progress}
\end{figure}

\begin{figure}
  \centering
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of correct \texttt{check-sat} answers (out
      of \num{30370517} total) within a time limit of \SI{2400}{s} on
      common benchmarks 2015--2018 of all logics in the \apptrack.}
    \label{fig:progress-all-app}
  \end{minipage}\hfill
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of number of unsat core reductions within a
      time limit of \SI{2400}{s} on common benchmarks 2016--2018 of
      all logics in the \ucoretrack.\\${}$}
    \label{fig:progress-all-uc}
  \end{minipage}
\end{figure}

@@

In many cases, an SMT application produces either mainly satisfiable or mainly
unsatisfiable queries to the SMT solver.  A typical example is bounded model checking,
where a query is only satisfiable if a property of the model does not hold.  As
a consequence, some solvers may implement specialized techniques and
optimizations for the more frequent (the expected) case.
%
Therefore, it is interesting to ask whether the winners of divisions of a track
might have changed if benchmarks in that division had been restricted to one of
these results.  Tables~\ref{tab:results:sat}-\ref{tab:results:unsat} show the
changes in division winners if only satisfiable or unsatisfiable results are
given. This table is in reference to Table~\ref{tab:winners-main} and only
lists a solver if the result has changed. A non-competing solver is listed by
itself if it was not the overall best performing solver of that division but
now outperforms the winning competitive solver, and the winning competing
solver did not change.
It is interesting to note that we see some new solvers winning divisions that did not win any division in the main results. For example, Alt-Ergo solves the most satisfiable benchmarks in AUFLIA and ALIA in 2018, and SMTInterpol performs very well on unsatisfiable benchmarks in QF\_LIA.

@@

Different application domains of SMT typically impose a wide range of time
limits (from hours to seconds). In domains with very low time limits, these
limits are, in the incremental case, usually even defined per incremental
query.  With 20 and 40 minutes, the time limits used in the competition for all
tracks in all four years were relatively long and the same for all benchmarks,
thus agnostic to the application domain of a benchmark.  Hence, it is
interesting to investigate how the results change if we consider a much shorter
time limit.  Table~\ref{tab:results:24s} shows the results of virtually
imposing a time limit of 24 seconds\footnote{This time limit is used for the
new 24 seconds score introduced in SMT-COMP 2019 and was inspired by a use case
at Amazon.} in the \maintrack.  As in the previous analysis, this highlights the
different winners under this new scheme only. Here we see STP winning a
division for the first time in our analysis (QF\_BV in 2016) and Yices2
performing well.

>>>>

%\usepackage{showframe}   % debug

@@

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
  \caption{VBS on common benchmarks 2015--2018 of all divisions in the
    \maintrack with a time limit of \SI{1200}{s}.  Number of common
    benchmarks is indicated with a gray vertical line.}
  \label{fig:progress-all}
\end{figure}

\begin{figure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2014-2015.pdf}}
    \caption{2014 vs.~2015}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2016.pdf}}
    \caption{2015 vs.~2016}
  \end{subfigure}
  \\[2ex]
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2016-2017.pdf}}
    \caption{2016 vs.~2017}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2017-2018.pdf}}
    \caption{2017 vs.~2018}
  \end{subfigure}
  \caption{VBS on common benchmarks for pairs of years of all \maintrack
  divisions with a time limit of \SI{1200}{s}.  Number of common benchmarks is
  indicated with a gray vertical line.}
  \label{fig:progress}
\end{figure}

\begin{figure}
  \centering
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of correct \texttt{check-sat} answers (out
      of \num{30370517} total) within a time limit of \SI{2400}{s} on
      common benchmarks 2015--2018 of all divisions in the \apptrack.}
    \label{fig:progress-all-app}
  \end{minipage}\hfill
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of number of unsat core reductions within a
      time limit of \SI{2400}{s} on common benchmarks 2016--2018 of
      all divisions in the \ucoretrack.\\${}$}
    \label{fig:progress-all-uc}
  \end{minipage}
\end{figure}

@@

In many cases, an SMT application produces either mainly satisfiable or mainly
unsatisfiable queries to the SMT solver.  A typical example is bounded model checking,
where a query is only satisfiable if a property of the model does not hold.  As
a consequence, some solvers may implement specialized techniques and
optimizations for the more frequent (the expected) case.
%
Therefore, it is interesting to ask whether the winners of divisions of a track
might have changed if benchmarks in that division had been restricted to one of
these results.  Tables~\ref{tab:results:sat}-\ref{tab:results:unsat} show the
changes in division winners if only satisfiable or unsatisfiable results are
given. These tables only lists the result for a division if it has changed
with respect to Table~\ref{tab:winners-main}. A non-competing solver is listed
by itself if there was no competing solver with a positive division score under
the given constraints.
It is interesting to note that we see some new solvers winning divisions that
did not win any division in the main results. For example, veriT solves the
most satisfiable benchmarks in QF\_UFIDL in 2018 and the most unsatisfiable
benchmarks in all four years in UFLRA, and SMTInterpol performs very well on
unsatisfiable benchmarks in QF\_LIA.

@@

Different application domains of SMT typically impose a wide range of time
limits (from hours to seconds). In domains with very low time limits, these
limits are, in the incremental case, usually even defined per incremental
query.  With 20 and 40 minutes, the time limits used in the competition for all
tracks in all four years were relatively long and the same for all benchmarks,
thus agnostic to the application domain of a benchmark.  Hence, it is
interesting to investigate how the results change if we consider a much shorter
time limit.  Table~\ref{tab:results:24s} shows the results of virtually
imposing a time limit of 24 seconds\footnote{This time limit is used for the
new 24 seconds score introduced in SMT-COMP 2019 and was inspired by a use case
at Amazon.} in the \maintrack.  As in the previous analysis, this highlights the
different winners under this new scheme only. Here we see Alt-Ergo (AUFLIRA in
2018) and STP (QF\_BV in 2016) winning a division for the first time in our
analysis, and Yices performing well.
